One-step, three-factor authentication with in-ear EEG

### 2016-12-05 paper.tex
Fixed tables

\begin{table}[h]
\caption{Set of tasks proposed for authentication with descriptions.}
\centering
\begin{tabular}{p{2.7cm}p{11cm}}
\hline
\textbf{Task} & \textbf{Description} \\
\hline
Breathe & Relaxed breathing with eyes closed.\\
Breathe - Open & Relaxed breathing with eyes open.\\
Sport & Imagining attempting a sport motion of participant's choice. \\
Song & Imagining a song of participant's choice playing. \\
Song - Open & Imagining a song of participant's choice playing with eyes open. \\
Speech & Imagining a phrase of participant's choice being spoken.\\
Listen - Tone & Listening to a continuous tone.\\
Listen - ASSR & Listening to noise modulated at 40 Hz.\\
Face & Imagining a person's face of participant's choice.\\
Sequence & Imagining a person's face, a number, and a word of participant's choice on timed cues.\\
\hline
\end{tabular}
\end{table}

\begin{table}[h]
\caption{Properties of authentication tasks. Tasks are listed vertically, and various properties of the tasks are listed horizontally,
with ones and zeroes denoting whether a task does or does not have that property, respectively.}
\begin{tabular}{p{2.7cm}p{1.7cm}p{1.7cm}p{1.7cm}p{1.7cm}p{1.7cm}p{1.7cm}p{1.7cm}}
\hline
\textbf{Task} & \textbf{External Stimuli} & \textbf{Chosen Secret} & \textbf{Eyes Closed} & \textbf{Motor Imagery} & \textbf{Visual Imagery} & \textbf{Audio Imagery} \\
\hline
Breathe & 0 & 0 & 1 & 0 & 0 & 0\\
Breathe - Open & 0 & 0 & 0 & 0 & 0 & 0\\
Sport & 0 & 1 & 1 & 1 & 0 & 0\\
Song & 0 & 1 & 1 & 0 & 0 & 1\\
Song - Open & 0 & 1 & 0 & 0 & 0 & 1\\
Speech & 0 & 1 & 1 & 0 & 0 & 1\\
Listen - Tone & 1 & 0 & 1 & 0 & 0 & 0\\
Listen - ASSR & 1 & 0 & 1 & 0 & 0 & 0\\
Face & 0 & 1 & 1 & 0 & 1 & 0\\
Sequence & 1 & 0 & 0 & 0 & 1 & 0\\
\hline
\end{tabular}
\end{table}

@@

For authentication analysis, we will build upon the analysis methodology and
tools from our previous studies. We will apply the logarithmic binning technique
that we have developed in [5] to the EEG power spectrum data during the signal
pre-processing step. We will then apply machine learning to train and test a
support vector classifier as in [4]. We will compare the results against the
threshold-based authentication protocol based on cosine similarity as in [2,3].
A key change for this study is that we will be able to collect up to 8 separate
channels of EEG data, including multiple channels from each ear. This is in
contrast to our previous studies, where we collected only a single channel of
EEG, either on the prefrontal cortex (FP1) location or in the ear canal. Therefore,
we will need to develop new analytic techniques to both (i) assess improvements
in authentication accuracy due to the increased channels of data, and (ii) assess
relative contributions of individual electrode locations to authentication accuracy.
Finally, we will evaluate the usability of custom-fit Ear EEG authentication along
several dimensions. They include the comfort and fit of the earpieces, the
preparatory steps of using the devices, the ease and repeatability of the
authentication tasks, and the recall rates of the personal secrets.
\section{{\bfseries\sffamily TODO} Preliminary results}
\label{sec:org914f392}

@@

\begin{table}[h]
\centering
\caption{Authentication accuracy for each sensor position. Left and right ears were a composite of three electrode positions along the helix, front of the ear canal, and back of the ear canal.}
\begin{tabular}{l|rr|rr|rr}
\textbf{Task} & \textbf{Left Ear} &  & \textbf{Right Ear} &  & \textbf{Fp1} & \\
\hline
 & \textbf{FAR} & \textbf{FRR} & \textbf{FAR} & \textbf{FRR} & \textbf{FAR} & \textbf{FRR}\\
\hline
Breathe & 0 & 0 & 0 & 0 & 0 & 0\\
Breathe - Open & 0.039 & 0 & 0 & 0 & 0 & 0\\
Sport & 0.039 & 0.036 & 0 & 0 & 0 & 0\\
Song & 0 & 0 & 0 & 0 & 0 & 0\\
Song - Open & 0 & 0 & 0 & 0 & 0 & 0\\
Speech & 0 & 0 & 0 & 0 & 0 & 0\\
Listen - Tone & 0 & 0 & 0 & 0.009 & 0 & 0\\
Listen - ASSR & 0 & 0 & 0 & 0 & 0 & 0\\
Face & 0 & 0 & 0 & 0.002 & 0 & 0\\
Sequence & 0 & 0 & 0 & 0 & 0 & 0\\
\end{tabular}
\end{table}

Finally, for each subject, for each task, we trained a binary classifier 
in the following manner: the right subject, performing the right task, were taken
as positive examples. The wrong person, performing any task, were taken as negative
examples. For a random, balanced subsample of those groups, we trained an ensemble
binary classifier with XGboost. For the remainder of the data, we tested the 
classifier's accuracy, measuring the false acceptance rate (FAR) and the false
rejection rate (FRR) (Table 1).

@@

\begin{table}[h]
\centering
\caption{FARs for right-person, wrong-task, and p-values corresponding to confidence that these FARs were drawn from the same distribution as from the right-person-right-task trials.}
\begin{tabular}{lrrr}
\textbf{Task} & \textbf{Right Ear} & \textbf{Left Ear} & \textbf{Fp1}\\
\hline
Breathe & 0 & 0.240 & 0\\
Breathe - Open & 0.254 & 0.129 & 0\\
Sport & 0.222 & 0.135 & 0\\
Song & 0 & 0.211 & 0\\
Song - Open & 0 & 0.166 & 0\\
Speech & 0.311 & 0.116 & 0\\
Listen - Tone & 0 & 0.333 & 0\\
Listen - ASSR & 0.322 & 0.078 & 0\\
Face & 0.355 & 0.055 & 0\\
Sequence & 0.433 & 0 & 0\\
\hline
\textbf{p-value} & \textbf{*0.0076} & \textbf{*0.009} & N/A\\
\end{tabular}
\end{table}

Our low p-values (Table 2) indicate that the passthought, as well as the inherence
factor associated with the custom-fit EEG earbud, both contribute to the classifier
performance discussed in Section 5.2. We are confident, then, in our claim that this work
could potentially yield multiple-factor authentication in a single step. However, we
will need to collect a great deal more data to substantiate this claim rigorously.

>>>>

\begin{table}[h]
\centering
\begin{tabular}{ll}
\textbf{\textbf{Task}} & \textbf{\textbf{Description}}\\
\hline
Breathe & Relaxed breathing with eyes closed.\\
Breathe - Open & Relaxed breathing with eyes open.\\
Sport & Sport-related motor imagery of participant's choice.\\
Song & Imagining a song of participant's choice playing.\\
Song - Open & Imagining a song with eyes open.\\
Speech & Imagining a phrase of participant's choice being spoken.\\
Listen & Tone \& Listening to a continuous tone.\\
Listen - ASSR & Listening to noise modulated at 40 Hz.\\
Face & Imagining a person's face of participant's choice.\\
Sequence & On timed cues, imagine a face, a number, and a word.\\
\hline
\end{tabular}
\caption{Set of tasks proposed for authentication with descriptions.}
\end{table}

\begin{table}[h]
\centering
\begin{tabular}{lllll}
Task & External stimuli? & Personal secret? & Eyes? & Imagery?\\
\hline
Breathe & No & No & Closed & None\\
Breathe - open & No & No & Open & None\\
Sport & No & Yes & Closed & Motor\\
Song & No & Yes & Closed & Aural\\
Song - open & No & Yes & Open & Aural\\
Speech & No & Yes & Closed & Aural\\
Listen - Tone & Yes & No & Closed & None\\
Listen - ASSR & Yes & No & Closed & None\\
Face & No & Yes & Closed & Visual\\
Sequence & Yes & Yes & Open & Visual\\
\hline
\end{tabular}
\caption{Properties of authentication tasks. We selected tasks with a variety of different properteries, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability, and user security.}
\end{table}

@@

For authentication analysis, we will build upon the analysis methodology and
tools from our previous studies. We will apply the logarithmic binning technique
that we have developed in [5] to the EEG power spectrum data during the signal
pre-processing step. We will then apply machine learning to train and test a
support vector classifier as in [4]. We will compare the results against the
threshold-based authentication protocol based on cosine similarity as in [2,3].
A key change for this study is that we will be able to collect up to 8 separate
channels of EEG data, including multiple channels from each ear. This is in
contrast to our previous studies, where we collected only a single channel of
EEG, either on the prefrontal cortex (FP1) location or in the ear canal. Therefore,
we will need to develop new analytic techniques to both (i) assess improvements
in authentication accuracy due to the increased channels of data, and (ii) assess
relative contributions of individual electrode locations to authentication accuracy.
Finally, we will evaluate the usability of custom-fit Ear EEG authentication along
several dimensions. They include the comfort and fit of the earpieces, the
preparatory steps of using the devices, the ease and repeatability of the
authentication tasks, and the recall rates of the personal secrets.
\section{Preliminary results}
\label{sec:org914f392}

@@

\begin{table}[h]
\centering
\begin{tabular}{l|rr|rr|rr}
\textbf{Task} & \textbf{Left Ear} &  & \textbf{Right Ear} &  & \textbf{Fp1} & \\
\hline
 & \textbf{FAR} & \textbf{FRR} & \textbf{FAR} & \textbf{FRR} & \textbf{FAR} & \textbf{FRR}\\
\hline
Breathe & 0 & 0 & 0 & 0 & 0 & 0\\
Breathe - Open & 0.039 & 0 & 0 & 0 & 0 & 0\\
Sport & 0.039 & 0.036 & 0 & 0 & 0 & 0\\
Song & 0 & 0 & 0 & 0 & 0 & 0\\
Song - Open & 0 & 0 & 0 & 0 & 0 & 0\\
Speech & 0 & 0 & 0 & 0 & 0 & 0\\
Listen - Tone & 0 & 0 & 0 & 0.009 & 0 & 0\\
Listen - ASSR & 0 & 0 & 0 & 0 & 0 & 0\\
Face & 0 & 0 & 0 & 0.002 & 0 & 0\\
Sequence & 0 & 0 & 0 & 0 & 0 & 0\\
\end{tabular}
\caption{Authentication accuracy for each sensor position. Left and right ears were a composite of three electrode positions along the helix, front of the ear canal, and back of the ear canal.}
\end{table}

Finally, for each subject, for each task, we trained a binary classifier 
in the following manner: the right subject, performing the right task, were taken
as positive examples. The wrong person, performing any task, were taken as negative
examples. For a random, balanced subsample of those groups, we trained an ensemble
binary classifier with XGboost. For the remainder of the data, we tested the 
classifier's accuracy, measuring the false acceptance rate (FAR) and the false
rejection rate (FRR) (Table 3).

@@

\begin{table}[h]
\centering
\begin{tabular}{lrrr}
\textbf{Task} & \textbf{Right Ear} & \textbf{Left Ear} & \textbf{Fp1}\\
\hline
Breathe & 0 & 0.240 & 0\\
Breathe - Open & 0.254 & 0.129 & 0\\
Sport & 0.222 & 0.135 & 0\\
Song & 0 & 0.211 & 0\\
Song - Open & 0 & 0.166 & 0\\
Speech & 0.311 & 0.116 & 0\\
Listen - Tone & 0 & 0.333 & 0\\
Listen - ASSR & 0.322 & 0.078 & 0\\
Face & 0.355 & 0.055 & 0\\
Sequence & 0.433 & 0 & 0\\
\hline
\textbf{p-value} & \textbf{*0.0076} & \textbf{*0.009} & N/A\\
\end{tabular}
\caption{FARs for right-person, wrong-task, and p-values corresponding to confidence that these FARs were drawn from the same distribution as from the right-person-right-task trials.}
\end{table}

Our low p-values (Table 4) indicate that the passthought, as well as the inherence
factor associated with the custom-fit EEG earbud, both contribute to the classifier
performance discussed in Section 5.2. We are confident, then, in our claim that this work
could potentially yield multiple-factor authentication in a single step. However, we
will need to collect a great deal more data to substantiate this claim rigorously.
